WasteAndMaterialFootprint: A python package to quantify supply chain flows of waste and material in LCA databases

### 2024-02-28 latex_files/cover_letter.tex
update name and readme
update

\begin{enumerate}
    \item {Reviewer 1 Name, Affiliation, Email Address}
    \item {Reviewer 2 Name, Affiliation, Email Address}
    \item {Reviewer 3 Name, Affiliation, Email Address}
\end{enumerate}
\vspace{1em}

@@

\closing{Sincerely,}
% Signature block with names in a row using dummy images for alignment
\begin{center}
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{signature_scm.png}\\ % Replace with your actual signature file name.
      Stewart Charles McDowall\\
    %   \textbf{Corresponding author}
    \end{minipage}%
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{dummy_signature.png}\\ % Invisible dummy image
      Elizabeth Lanphere
    \end{minipage}%
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{dummy_signature.png}\\ % Invisible dummy image
      Stefano Cucurachi
    \end{minipage}%
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{dummy_signature.png}\\ % Invisible dummy image
      Carlos Felipe Rocha Blanco
    \end{minipage}
  \end{center}

>>>>

\begin{enumerate}
    \item {Rafael Laurenti, IVL --- Swedish Environmental Research Institute, rafa@kth.se}
    \item {Valentina Bisinella,  DTU --- Technical University of Denmark, valenb@dtu.dk}
    \item {Reviewer 3 Name, Affiliation, Email Address}
\end{enumerate}
\vspace{1em}

@@

\closing{Sincerely,}
% Signature block with names in a row using dummy images for alignment
\begin{center}
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{signature_scm.png}\\ % Replace with your actual signature file name.
      Stewart Charles McDowall\\
    %   \textbf{Corresponding author}
    \end{minipage}%
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{dummy_signature.png}\\ % Invisible dummy image
      Elizabeth Lanphear
    \end{minipage}%
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{dummy_signature.png}\\ % Invisible dummy image
      Stefano Cucurachi
    \end{minipage}%
    \begin{minipage}[t]{0.25\textwidth}
      \centering
      \vspace{-2cm}
      \includegraphics[height=2cm]{dummy_signature.png}\\ % Invisible dummy image
      Carlos Felipe Rocha Blanco
    \end{minipage}
  \end{center}

### 2024-02-28 latex_files/main.tex
update name and readme
update

    \title{WasteAndMaterialFootprint: A python package to quantify supply chain flows of waste and material in LCA databases}
    \author[1]{Stewart Charles McDowall\corref{cor1}}
    \ead{s.c.mcdowall@cml.leidenuniv.nl}
    \author[1]{Elizabeth Lanphere}
    \author[1]{Stefano Cucurachi}
    \author[1]{Carlos Felipe Blanco}

@@

        The `circular economy' is a concept focused on the prevention of waste and the reuse of resources. Thus, identifying and quantifying waste and material flows are of fundamental importance. Life Cycle Assessment (LCA) is powerful for this end, given its capacity to pinpoint hotspots of environmental impact throughout the life cycle of products and services, those where the implementation of circular principles could be most effective.

@@

        A case study on battery supply chains demonstrates the tool's utility. WasteAndMaterialFootprint quantifies and compares demands and potential environmental impacts, aiding sustainable decision-making. It contributes to a more sustainable, circular economy by providing detailed material usage and waste generation analysis.

@@

\section*{CRediT authorship contribution statement}
\cbox{Co-authors, please check this and change as necessary.}
\textbf{Stewart Charles McDowall:} Methodology, Software, Validation, Formal analysis, Investigation, Data curation, Writing - original draft, Writing - review \& editing, Visualization.
\textbf{Elizabeth Lanphere:} Conceptualization, Methodology, Software, Validation, Writing - review \& editing.
\textbf{Stefano Cucurachi:} Conceptualization, Writing - review \& editing, Supervision, Project administration, Funding acquisition.
\textbf{Carlos Felipe Blanco:} Conceptualization, Writing - review \& editing, Supervision, Project administration, Funding acquisition.

>>>>

    \title{WasteAndMaterialFootprint: A python package to quantify supply chain flows of waste and material in LCA databases}
    \author[1]{Stewart Charles McDowall\corref{cor1}}
    \ead{s.c.mcdowall@cml.leidenuniv.nl}
    \author[1]{Elizabeth Lanphear}
    \author[1]{Stefano Cucurachi}
    \author[1]{Carlos Felipe Blanco}

@@

        The `circular economy' is a concept centered on `re-X' strategies---on the prevention of waste and the reuse of resources. Thus, identifying and quantifying waste and material flows are of fundamental importance. Life Cycle Assessment (LCA) is powerful for this end, given its capacity to pinpoint hotspots of environmental impact throughout the life cycle of products and services, those where the implementation of circular principles could be most effective.

@@

        A case study on battery supply chains demonstrates the tool's utility. WasteAndMaterialFootprint quantifies and compares inventory demands and potential environmental burdens, aiding sustainable decision-making. It contributes to a more sustainable, circular economy by providing detailed material usage and waste generation analysis.

@@

\section*{CRediT authorship contribution statement}
\cbox{Co-authors, please check this and change as necessary.}
\textbf{Stewart Charles McDowall:} Methodology, Software, Validation, Formal analysis, Investigation, Data curation, Writing - original draft, Writing - review \& editing, Visualization.
\textbf{Elizabeth Lanphear:} Conceptualization, Methodology, Software, Validation, Writing - review \& editing.
\textbf{Stefano Cucurachi:} Conceptualization, Writing - review \& editing, Supervision, Project administration, Funding acquisition.
\textbf{Carlos Felipe Blanco:} Conceptualization, Writing - review \& editing, Supervision, Project administration, Funding acquisition.
